---
title: "Doing Data Science, HomeWork Week 4: Bootstrap Showing CLT"
author: "Najeeb Zaidi"
date: "August 5, 2016"
output: 
  html_document: 
    keep_md: yes
    theme: spacelab
---

```{r ex="bootstarp", type="pre-exercise-code"}
rm(list = ls()) 
objects()
getwd() 
setwd("C:\\Users\\najee\\Documents\\R\\MSDS6306-W4-HW")

library(ggplot2)
library(stats)
library(utils)
library(tutorial)
library(googleVis)
library(graphics)

tutorial::go_interactive()

```
_Note: we could hide this chunk by adding include=FALSE, echo=FALSE in the first line_


# Introduction
In this presentation, we attempt to illustrate the Central Limit Theorem using the Bootstrap Method or Simulation Method on a sample data set.

We also describe the advantage of using this technique when compared to other methods .

This HTML uses DataCamp Interactive to display the R code used and is the improved version of plain text file presented earlier.

## Central Limit Theorem (CLT)
[describe]

## Bootstrap / Simulation Method
[describe]

## Illustrations

The first illustration below uses the Parametric Bootstrap.
We use a random sample of x & y observations and define the number of simulations as well as set the seed to ensure results are replicated at a later stage:

```{r ex="bootstarp", type="sample-code"}

x <- c(187, 169, 123, 166, 199, 127, 159, 155, 145, 142, 171)
y <- c(122, 45, 98, 38, 148, 179, 193, 54, 22, 245)

n1 <- length(x)
n2 <- length(y)

# Set number of Simulations 
k <- 10000

# define seed number such that the following computations can be replicated or reproduced
set.seed(1234)
```


```{r ex="bootstarp", type="solution"}

# Simulate or Bootstrap with replacement by repliocating from k samples of n1 & n2 normal 
# distributions with the right mean and variance 
# Also called the Parametric Bootstrap

simXsample <- replicate(k, rnorm(n1, mean(x), sd(x)))
simYsample <- replicate(k, rnorm(n2, mean(x), sd(x)))

# Compute mean differences of the n1 & n2 simulated observations k times

simMeanDifs <- apply(simXsample, 2, mean) - apply(simYsample, 2, mean)

# find the two relevant quantiles of k simulated mean differences
# i.e. 95% CI 
quantile(simMeanDifs, c(0.025 , 0.975))

```
The Histogram plot of simulated mean differences looks like this:

```{r ex="bootstarp", type="sct"}
# Plot
hist(simMeanDifs, col = c("green"))

```




